---
title: "Total solar irradiance according to ISO 52010-1:2017"
author: "Lukas Lundström"
date: '2019-03-05'
output: github_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/img/README-"
)
```

## Introduction

Total solar irradiance on a surface with arbitrary orientation and tilt, calculated according to ISO 52010-1:2017 [\[2\]][2]. This code was originally developed as part of this article [\[1\]][1]. 

Currently only available via GitHub, you install it by: 
```{r, warning=FALSE}
if (!require('devtools')) install.packages('devtools')
devtools::install_github("lukas-rokka/solarCalcISO52010")
library(solarCalcISO52010)
```
https://github.com/lukas-rokka/ISO14N_example has some further example code on how to use this package for building energy simulation purposes. The [`camsRad` R-package](https://github.com/ropensci/camsRad) can be used to acquire satellite-based solar irradiance data from [CAMS](http://www.soda-pro.com/web-services/radiation/cams-radiation-service).

## References

1. Lundström, Lukas, Jan Akander, and Jesús Zambrano. 2019. "Development of a Space Heating Model Suitable for the Automated Model Generation of Existing Multifamily Buildings -- A Case Study in Nordic Climate". Energies 12 (3).  https://doi.org/10.3390/en12030485

2. ISO 52016-1:2017. "Energy performance of buildings -- External climatic conditions -- Part 1: Conversion of climatic data for energy calculations (ISO 52010-1:2017)" https://www.iso.org/standard/65703.html


[1]: https://doi.org/10.3390/en12030485 "Lundström, Lukas, Jan Akander, and Jesús Zambrano. 2019. Development of a Space Heating Model Suitable for the Automated Model Generation of Existing Multifamily Buildings -- A Case Study in Nordic Climate. Energies 12 (3)."

[2]: https://www.iso.org/standard/65703.html "Energy performance of buildings -- External climatic conditions -- Part 1: Conversion of climatic data for energy calculations (ISO 52010-1:2017)."

